Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-03-14 paperDistance/paper.tex
bugfix

% # To-do list
% - We need a standard name for the \tgas--\tmass\ Intersection.
% - zeroth draft the introduction
% - zeroth draft the method section
% - zeroth draft the assumptions list
% - reformat single-column

@@

It wouldn't be using the data twice---that is, it would be valid from a
probabilistic perspective---if we performed a full hierarchical Bayesian
inference.
Exploration of that possibility, and its computational tractability,
is among our long-term goals and motivations.
Along those lines, this paper can be seen as a companion to
a related project (CITE BORIS), in which we use a
somewhat less flexible model for the \cmd, but in which we take a much more principled
approach to the inference.

@@

\begin{equation}
\label{eq:data}
\begin{aligned}
\mathrm{data vector} \;\;\;\; &\vec{y} = [10^{0.2M_{J,n}}, (J- K)_n] \;  n \in \mathrm{stars} \\
\mathrm{with \; absolute \; magnitude} \;\;\;\; &M_{J,n} = J_n - DM_n - Q_JE(B-V)_n \\
& DM_n = -5\mathrm{log_{10}}\frac{1}{\varpi} \\
\mathrm{and \; color} \;\;\;\; &(J - K)_n = J_n - K_n - Q_{JK}E(B-V)_n

\end{aligned}
\end{equation}

@@

>>>>

%@archiver{PUT FIGURE NAME HERE}

% # To-do list
% - We need a standard name for the \tgas--\tmass--\PanSTARRS\ Intersection.
% - zeroth draft the introduction
% - zeroth draft the method section
% - zeroth draft the assumptions list
% - reformat single-column

@@

It wouldn't be using the data twice---that is, it would be valid from a
probabilistic perspective---if we performed a full hierarchical Bayesian
inference.
Exploration of that possibility, and its computational tractability,
is among our long-term goals and motivations.
Along those lines, this paper can be seen as a companion to
a related project (CITE BORIS), in which we use a
slightly less appropriate model for the \cmd, but in which we take a much more principled
approach to the inference.

@@

\begin{equation}
\label{eq:data}
\begin{aligned}
\mathrm{data vector} \;\;\;\; &\vec{y} = [10^{0.2M_{J,n}}, (J- K)_n] \;  n \in \mathrm{stars} \\
\mathrm{with \; absolute \; magnitude} \;\;\;\; &M_{J,n} = J_n - DM_n - Q_JE(B-V)_n \\
& DM_n = -5\log_{10}\frac{1}{\varpi} \\
\mathrm{and \; color} \;\;\;\; &(J - K)_n = J_n - K_n - Q_{JK}E(B-V)_n
\end{aligned}
\end{equation}

@@

Talk about structures in CMD; red bump - acknowledge Ana ! s
What's That Feature ?!!

Fraction of stars in various parts of the diagram?

Compare with literature stellar models
